\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual Multi-Loop Integrands

### 2023-09-21 notes/2loopNLSM.tex
l -> \ell in appendix C

Here we apply the same conventions of Ref.~\cite{jjmcTASI2014}, which we quote now. The component definition of our spinor bracket that are consistent with the conventions above,

@@

where the $a_i$ are component values of the four-vector, $k^\mu_a = (a_0,a_1,a_2,a_3)$. For massless momenta, $k_a$ and $k_b$, one can apply the on-shell condition, $k_a^2=k_b^2=0$, and show that:

@@

Four-dimensional polarization dot products with fixed helicity states can be mapped as follows:

@@

Note that given the above definition, the spinor helicity variables carry the same mass dimension for both the angle and square brackets. In terms of light-cone coordinates that we employed above in \cref{sec:CKLagrangians}, the angles and squares can be rewritten as follows:

@@

The conventions we use in the text where the holomorphic spinor, $X(p,k)$, carries extra mass dimension essentially amounts to shifting the bracket by the following overall factor:

@@

At one-loop, weight counting tells us that the $n$-gon master numerator must have $n$ on-shell $Z$-particles. Unitarity requires that there are three distinct contributions from $Y\!Z$ theory -- the first from an off-shell $Y$-loop particle and then two more from different orientations of a $\bar{Z}Z$-loop.  Thus, $YZ$ theory gives us the following one-loop $n$-gon numerator:

@@

where $(\,\cdots)$ indicates an internal contraction over the $YY$ and $\bar{Z}Z$ loops. Plugging in the Feynman rule of \cref{eq:FeynmanRuleYYZ} and \cref{eq:FeynmanRuleXZZ}, we can readily obtain expressions in terms of the internal loop factors $l_i$ and the external momenta $k_i$ (we define the $l_i$ loop momentum as that flowing into $k_i$ and out of $k_{i-1}$):

@@

N_{(12...n)}^{\text{NLSM}}=(T^{1}T^{2}\cdots T^{n}) = (l_1 k_1)(l_2 k_2) \cdots (l_n k_n)

@@

 (F^1F^2\cdots F^n) = D (l_1 k_1)(l_2 k_2) \cdots (l_n k_n) + \mathcal{O}(D^0)

@@

The dimension dependent factor essentially counts that number of internal vector states. While this $n$-gon is manifestly color-dual, it does not produce the right cuts for NLSM. However, the scalar contribution, that comes dressed with an overall factor $D$ \textit{does} manifest the duality globally, and satisfies all the desired pion cuts. In order for the Feynman rules for $Y\!Z$ theory compute one-loop color-dual numerators consistent with NLSM cuts, we must add some additional states to cancel off he spurious poles, while preserving color-kinematics duality. We leave this as a direction of future work.

While the $\bar{Z}Z$ vector loop spoils color-kinematics off-shell, the $Y\!Z$ loop alone gives us a desired expression for the $n$-gon. The important takeaway is that we now have a guess for the form of the off-shell three-point vertex that has a chance of manifesting the duality off-shell. The $n$-gon numerator above has scalar insertions of the following kinematic vertex:
\begin{equation}
T^{a}_{LR} = k_a(l_L-l_{R}) = (l_L+l_{R}) (l_L-l_{R})  = l_L^2-l_{R}^2 
\end{equation}
Given this structure, in the next section we will attempt to construct two-loop basis diagrams from these cubic vertex assignments and try to reverse engineer the particle content that produces these master numerators.

Before proceeding, we note a strange property of the $n$-gon numerator for the pions. In this form, Jacobi relations produce \textit{non-vanishing} values for bubbles on external legs (BELs). However, it is easy to see that the contribution integrates to zero after applying IBP relations/tensor reduction on the bubble. The BEL diagram can be reconstructed from the $n$-gon as follows:
\begin{equation}
N^{\text{BEL}}_{1|2,34} = N^{\text{NLSM}}_{(1234,l)}-N^{\text{NLSM}}_{(1243,l)}-N^{\text{NLSM}}_{(1342,l)}+N^{\text{NLSM}}_{(1432,l)}
\end{equation}
where we define the loop momentum to be in between the left most and right most leg on the box. Plugging in particular values for $l_i$, we obtain the following expression for the BEL
\begin{equation}
N^{\text{BEL}}_{1|2,34} = s_{12} (l+k_1)^2 l^{\mu} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} 
\end{equation}
Notice there is an overall factor that cancels one of the propagators. Plugging this in, produces an integral of the following form
\begin{equation}
\mathcal{I}^{\text{BEL}}_{1|2,34} = s_{12} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} \int \frac{d^D l}{i\pi^{D/2}} \frac{l^\mu }{l^2-\mu^2} \sim   s_{12}(s_{13}-s_{14}) (\mu^2)^{D/2}
\end{equation}
where we have introduced a mass regulator that will be proportional the the on-shell momentum inside the BEL, $\mu^2 \equiv k_1^2$. Thus, in large enough dimension, this integral suppresses the $\mu^{-2}$ divergence appearing in the denominator of the BEL diagram.

>>>>

Here we apply the same conventions of Ref.~\cite{jjmcTASI2014}, which
we quote now. The component definition of our spinor bracket that are
consistent with the conventions above,

@@

where the $a_i$ are component values of the four-vector,
$k^\mu_a = (a_0,a_1,a_2,a_3)$. For massless momenta, $k_a$ and $k_b$,
one can apply the on-shell condition, $k_a^2=k_b^2=0$, and show that:

@@

Four-dimensional polarization dot products with fixed helicity states
can be mapped as follows:

@@

Note that given the above definition, the spinor helicity variables
carry the same mass dimension for both the angle and square
brackets. In terms of light-cone coordinates that we employed above in
\cref{sec:CKLagrangians}, the angles and squares can be rewritten as
follows:

@@

The conventions we use in the text where the holomorphic spinor,
$X(p,k)$, carries extra mass dimension essentially amounts to shifting
the bracket by the following overall factor:

@@

At one-loop, weight counting tells us that the $n$-gon master
numerator must have $n$ on-shell $Z$-particles. Unitarity requires
that there are three distinct contributions from $Y\!Z$ theory -- the
first from an off-shell $Y$-loop particle and then two more from
different orientations of a $\bar{Z}Z$-loop.  Thus, $YZ$ theory gives
us the following one-loop $n$-gon numerator:

@@

where $(\,\cdots)$ indicates an internal contraction over the $YY$ and
$\bar{Z}Z$ loops. Plugging in the Feynman rule of
\cref{eq:FeynmanRuleYYZ} and \cref{eq:FeynmanRuleXZZ}, we can readily
obtain expressions in terms of the internal loop factors $\ell_i$ and the
external momenta $k_i$ (we define the $\ell_i$ loop momentum as that
flowing into $k_i$ and out of $k_{i-1}$):

@@

N_{(12...n)}^{\text{NLSM}}=(T^{1}T^{2}\cdots T^{n}) = (\ell_1 k_1)(\ell_2 k_2) \cdots (\ell_n k_n)

@@

 (F^1F^2\cdots F^n) = D (\ell_1 k_1)(\ell_2 k_2) \cdots (\ell_n k_n) + \mathcal{O}(D^0)

@@

The dimension dependent factor essentially counts that number of
internal vector states. While this $n$-gon is manifestly color-dual,
it does not produce the right cuts for NLSM. However, the scalar
contribution, that comes dressed with an overall factor $D$
\textit{does} manifest the duality globally, and satisfies all the
desired pion cuts. In order for the Feynman rules for $Y\!Z$ theory
compute one-loop color-dual numerators consistent with NLSM cuts, we
must add some additional states to cancel off he spurious poles, while
preserving color-kinematics duality. We leave this as a direction of
future work.

While the $\bar{Z}Z$ vector loop spoils color-kinematics off-shell, the $Y\!Z$ loop alone gives us a desired expression for the $n$-gon. The important takeaway is that we now have a guess for the form of the off-shell three-point vertex that has a chance of manifesting the duality off-shell. The $n$-gon numerator above has scalar insertions of the following kinematic vertex:
\begin{equation}
T^{a}_{LR} = k_a(\ell_L-\ell_{R}) = (\ell_L+\ell_{R}) (\ell_L-\ell_{R})  = \ell_L^2-\ell_{R}^2 
\end{equation}
Given this structure, in the next section we will attempt to construct two-loop basis diagrams from these cubic vertex assignments and try to reverse engineer the particle content that produces these master numerators.

Before proceeding, we note a strange property of the $n$-gon numerator for the pions. In this form, Jacobi relations produce \textit{non-vanishing} values for bubbles on external legs (BELs). However, it is easy to see that the contribution integrates to zero after applying IBP relations/tensor reduction on the bubble. The BEL diagram can be reconstructed from the $n$-gon as follows:
\begin{equation}
N^{\text{BEL}}_{1|2,34} = N^{\text{NLSM}}_{(1234,\ell)}-N^{\text{NLSM}}_{(1243,\ell)}-N^{\text{NLSM}}_{(1342,\ell)}+N^{\text{NLSM}}_{(1432,\ell)}
\end{equation}
where we define the loop momentum to be in between the left most and right most leg on the box. Plugging in particular values for $\ell_i$, we obtain the following expression for the BEL
\begin{equation}
N^{\text{BEL}}_{1|2,34} = s_{12} (\ell+k_1)^2 \ell^{\mu} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} 
\end{equation}
Notice there is an overall factor that cancels one of the propagators. Plugging this in, produces an integral of the following form
\begin{equation}
\mathcal{I}^{\text{BEL}}_{1|2,34} = s_{12} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} \int \frac{d^D \ell}{i\pi^{D/2}} \frac{\ell^\mu }{\ell^2-\mu^2} \sim   s_{12}(s_{13}-s_{14}) (\mu^2)^{D/2}
\end{equation}
where we have introduced a mass regulator that will be proportional the the on-shell momentum inside the BEL, $\mu^2 \equiv k_1^2$. Thus, in large enough dimension, this integral suppresses the $\mu^{-2}$ divergence appearing in the denominator of the BEL diagram.
